\textbf{Empirical Bayes shrinkage, and denoising of Poisson and heteroskedastic Gaussian signals}

### 2016-03-03 paper/draft_7.tex
added draft 7, which updated simulations section and fixed parts of tex

Here we briefly outline the adaptive shrinkage method; see \cite{stephens:2015} for full details.
Adaptive shrinkage (\ash) is an EB method
for estimating quantities $\beta=(\beta_1,\dots,\beta_n)$ from noisy estimates 
$\bhat=(\bhat_1,\dots,\bhat_n)$ and their corresponding standard errors $\shat = (\shat_1,\dots,\shat_n)$. 
In its simpest form it assumes the hierarchical model
\begin{align}
\beta_j \| \shat_j & \sim g \\
\bhat_j \| \beta_j, \shat_j & \sim N(\beta_j, \shat_j^2),
\end{align}
where the distribution $g$ is constrained to be unimodal and symmetric. This constraint on $g$ can
be flexibly achieved using 
a mixture of zero-centered normal distributions

@@

A crucial question is, of course, how much to shrink. A key idea behind ash is that the shrinkage is ``adaptive", in that it
determined by the data, in two distinct ways. First, if at a particular scale many observed WCs are ``large" (compared with their standard errors)
then ash infers that, at this scale, many of the true WCs may also be large - that is, the estimated distribution $g$ in (\ref{}) will have a long tail.
Consequently ash will shrink less at this scale than at scales where few observed
WCs are large, for which the estimated $g$ will have a short tail. This is illustrated in panels b-c: at scale 1, many observed WCs are large (b), and so very little shrinkage is applied to these estimates (c).
In contrast, at scale 7, few observed WCs are large (b), and so stronger shrinkage is applied (c). Second, the shrinkage is adaptive to 
the standard error for each WC: at a given scale, WCs with larger standard error are shrunk more strongly than WCs with small standard error.
This is illustrated in panel d). (The standard errors vary among WCs here because of the hetereskedastic variance.)

@@

For the Gaussian case, we focus on mean estimation, initially with homoskedastic errors. We modelled our simulation study after
\cite{Antoniadis2001Wavelet}, using many of the same test functions, a variety of sample sizes, two different signal to noise ratios (SNRs), and including
the best-performing methods from their comparison. In particular their results showed that Translation Invariant (TI) thresholding (\cite{Coifman1995Translationinvariant}) performed the best for most of the test signals, where performance is measured by mean squared error (MSE). We also considered the Empirical Bayes shrinkage procedure (\cite{Johnstone2005Empirical}), named Ebayesthresh. 
All the methods were applied using the Symmlet8 wavelet basis \cite{}.

@@

We simulated data under two different scenarios:
\begin{enumerate}
\item We generated $n=500$ independent $(X_i,Y_i)$ pairs, with $X_i \sim$ Uniform(0,1), and $Y_i | X_i=x_i \sim N(m(x_i),s(x_i)^2)$
where $m(\cdot)$ and $s(\cdot)$ denote the mean and standard deviation functions (Figure \ref{fig:mfvb_eg}). We measured performance by the MSE 
evaluated at 201 equally spaced points on $(X_{min},X_{max})$ for both the mean and the standard deviation.
\item We generated $n=1024$ independent $(X_i,Y_i)$ pairs, with the $X_i$'s (deterministically) equally spaced on (0,1), and $Y_i|X_i$ as above. Performance is measured by MSE evaluated at the 1024 $X_i$'s for both the mean and the standard deviation.
\end{enumerate}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{mfvb_eg.pdf}
    \caption{Shows the mean function $m(x)$ $\pm$2 standard deviations $s(x)$ used in the simulation study comparing SMASH against MFVB. These functions correspond to mean and standard deviation functions (A) from \cite{Menictas2015Variational}.}
    \label{fig:mfvb_eg}
\end{figure}

@@

We compared SMASH with eight other methods, but we focus here on the comparisons with the best-performing other methods, which are Haar-Fisz (HF) (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}). The latter, like SMASH, is an Empirical Bayes method,  but with a less flexible prior distribution on the
multi-scale coefficients. The HF method involves first performing a transformation on the Poisson counts, and applying Gaussian wavelet methods to the transformed data. 
There are many choices for Gaussian wavelet methods, and the performance depends on these choices (and with different choices being optimal for different data sets). 
The settings we used here are documented in Supplementary Information, and were chosen by us to optimize (average) performance through moderately extensive experimentation on a range of simulations.

In summary, SMASH outperformed both HF and BMSM in the majority of simulations, with the gain in accuracy being strongest for the more challenging lower-intensity
scenarios. A typical result is shown in Figure \ref{fig:pois_sim}, with complete results in Supplementary Information (\url{?}). 
Among the other two methods, BMSM tends to be the more consistent performer. HF, with the settings
we used here, performs quite variably, being worse than the other two in most scenarios, but occassionally performing the best (specifically for the Angles, Bursts and Spikes test functions,
with (min,max) intensity (1/128,128)). As noted above, the HF transform can be used with many settings, so the results here should be viewed as a guide to the 
performance that can be achieved in practice.

%Besides the somewhat strong assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz. Here we analyzed primary resolution levels of 4, 5, 6 and 7, similar to \cite{Besbeas2004Comparative}. On the other hand, SMASH outperforms BMSM consistently, even though it is based on the same likelihood factorization used in the latter. We can thus conclude that the choice of ASH as the shrinkage procedure is superior to that used in BMSM in the simulation study. More importantly, using this formulation in SMASH also makes it easily extensible to multiple samples in the context of a (generalized) linear model, something we will briefly describe in the Discussion section.
\begin{figure}
\centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{violin_pois_1.pdf}
        \caption{}
        \label{fig:pois_1}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{violin_pois_8.pdf}
        \caption{}
        \label{fig:pois_8}
    \end{subfigure}
    \caption{Comparison of methods for denoising Poisson data (for the ``Bursts'' test function). The violin plots show distributions of MISE for each method over 100 datsets, with smaller values indicating better performance. The dashed green line indicates the median MISE for SMASH. Panel a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8).}
    \label{fig:pois_sim}
\end{figure}

One disadvantage of the HF transform is that, to achieve translation invariance (TI), the transform has to be done explicitly for each shift of the data: the tricks usually used to do this efficiently \cite{coifman.donoho.titable} do not work here. Thus, making HF fully translation invariant increases computation by a factor of $T$, rather than the factor of $\log(T)$ for the other methods. Here we follow advice in \cite{} to reduce the computational burden by averaging over 50 shifts of the data rather than $T$. Even so, HF was substantially slower than the other methods.
 A direct comparison of computational efficiency between SMASH and BMSM is difficult, as they are coded in different programming environments. Nevertheless, similarities between the two methods suggest that they should have similar computational cost.
 Both SMASH and BMSM took, typically, less than a second per dataset in our simulations.

@@

To further illustrate our Poisson de-noising procedure we applied it to data from genomic sequencing. Specifically we applied SMASH to chromatin immunoprecipitation sequencing (ChIP-seq) data for the transcription factor {\it YY1} in cell line GM12878
collected by the ENCODE (\textbf{Enc}yclopedia \textbf{O}f \textbf{D}NA \textbf{E}lements) project. 
The data (e.g.~Figure \ref{fig:seq_peak_data}) consist of counts of sequencing reads mapping to each location in genome. These can be treated as
arising from an inhomogeneous Poisson process, whose intensity at base $b$ is related to the strength of the binding 
of the transcription factor near $b$. Because binding tends to be quite localized, the intensity is low on average (the vast majority of 
counts are 0), but has a small number of intense ``peaks". Identifying these peaks can help discover regions where 
binding occurs, which is an important component of understanding gene regulation. Consequently there are
many methods published for ``peak detection" in ChIP-Seq data \cite{wilbanks:2010}.

@@

To illustrate this idea we applied SMASH to ChIP-seq data from a region of length $2^{15} (\approx 33k)$ basepairs from chromosome 1
(hg18 (or 19?) chr1:880001-1011072). The estimated intensity is shown in Figure \ref{fig:seq_peak_est}, overlaid on peaks called by
the popular peak calling software MACS \cite{}. We see that the locations with the strongest SMASH intensity estimates 
corresponds to peaks found by MACS.
However, the intensity estimate also suggests the presence of several additional weaker peaks not identified by MACS.

@@

With some work, our methods could also be extended to higher dimensions, where a wider range of applications is possible. For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in \cite{Nowak1999Multiscale}. However, recent research in image denoising problems has shown that smooth curves present in many images such as photographs might render wavelet transformations undesirable \cite{}. We could thus incorporate ASH into other types of transformations such as curvelets \cite{}, which would be a potential direction for future work.
\newpage
\section{Reference}

@@

With $\bm{Z}$ as defined in \eqref{eq:varobs1}, we apply the wavelet transform $W$ to $\bm{Z}^2$, and obtain the wavelet coefficients $\bm{\Gd}=W\bm{Z}^2$. Note that $\mathbb{E}(\bm{\Gd})=(\bm{\Gg})$, where $\bm{\Gg}=W\bm{\s}^2$. As with \eqref{eq:likelihood}, we treat the likelihood for $\bm{\Gg}$ as if it were independent, resulting in
\begin{eqnarray}
L(\bm{\Gg}|\bm{\Gd})=\prod_{j=0}^J\prod_{k=0}^{T-1}P(\Gd_{jk}|\Gg_{jk})
\end{eqnarray}
However, the likelihoods $L(\Gg_{jk}|\Gd_{jk})$ are not normal, and have no simple closed form expressions. As such, we approximate the likelihood by a normal likelihood through matching the moments of a normal distribution to the distribution $P(\Gd_{jk}|\Gg_{jk})$ i.e.
\begin{eqnarray}
P(\Gd_{jk}|\Gg_{jk})\approx N(\Gg_{jk},\hat{\mathbb{V}}(\Gd_{jk}))
\end{eqnarray}
so that
\begin{eqnarray}\label{eq:gaus approx}
L(\Gg_{jk}|\Gd_{jk})\approx \phi(\Gd_{jk};\Gg_{jk},\mathbb{V}(\Gd_{jk}))
\end{eqnarray}
where $\phi$ is the normal density function, and $\mathbb{V}(\Gd_{jk})$ is the variance of the detail coefficients. Since these variances are unknown, we estimate them from the data and then proceed to treat them as known. More specifically, since $Z_t\sim N(0,\s_t^2)$, we have that
\begin{eqnarray}
&\mathbb{E}(Z_t^4)\approx 3\s_t^4\notag\\
\label{eq:varvarest}\Rightarrow&\mathbb{V}(Z_t^2)\approx 2\s_t^4
\end{eqnarray}
and so we simply use $\frac{2}{3}Z_t^4$ as an unbiased estimator for $\mathbb{V}(Z_t^2)$. It then follows that $\hat{\mathbb{V}}(\Gd_{jk})$ is given by $\sum_{l=1}^n \frac{2}{3}Z_l^4W_{jk,l}^2$, and is unbiased for $\mathbb{V}(\Gd_{jk})$. These will be the inputs to ASH, which then produces shrunk estimates in the form of posterior means for the corresponding parameters. Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the detail coefficients at the finer levels. This is likely because the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points). One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH). The final estimate of the variance function is obtained from the posterior means via the average basis inverse across all the shifts.

@@

Note here that for the reconstructed signal to possess the property of shift invariance (see Coifman \& Donoho (1995)), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see \cite{Coifman1995Translationinvariant}, and \cite{Kolaczyk1999Multiscale}) rather than as described above. The idea remains the same however, and we can simply think of the extra $\Ga$'s as being defined similarly as the original $\Ga$'s, albeit from a shifted version of the original data points. To be more specific, the TI table contains the $\Ga_{jk}$ for all circulant shifts of the signal. Here we define the $t$-th shift of the signal $\bm{Y}$, denoted by $\bm{Y}^{(t)}$, to be created from $\bm{Y}$ itself by moving the first $n-t$ elements of $\bm{Y}$ $t$ positions to the right and then putting the last $t$ elements of $\bm{Y}$ in the first $t$ locations. Using this table, we are essentially computing the posterior expectations in \eqref{eq:Eproduct}-\eqref{eq:E2product} by averaging over all posterior expectations for every shift of the original signal ie.
\begin{eqnarray}
\label{eq:TIapproxexp}\frac{1}{n}\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})
\end{eqnarray}
which is an approximation to the true quantity we wish to compute, given by
\begin{eqnarray}
E(\hat{\Gl}_k)=\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})P(\mbox{$t$-th shift})
\end{eqnarray}
\end{appendices}

>>>>

Here we briefly outline the adaptive shrinkage method; see \cite{stephens:2015} for full details.
Adaptive shrinkage (\ash) is an EB method
for estimating quantities $\beta=(\beta_1,\dots,\beta_n)$ from noisy estimates 
$\bhat=(\bhat_1,\dots,\bhat_n)$ and their corresponding standard errors $\shat = (\shat_1,\dots,\shat_n)$. 
In its simpest form it assumes the hierarchical model
\begin{align}
\label{eq:ash_model_1}\beta_j \| \shat_j & \sim g \\
\bhat_j \| \beta_j, \shat_j & \sim N(\beta_j, \shat_j^2),
\end{align}
where the distribution $g$ is constrained to be unimodal and symmetric. This constraint on $g$ can
be flexibly achieved using 
a mixture of zero-centered normal distributions

@@

A crucial question is, of course, how much to shrink. A key idea behind ash is that the shrinkage is ``adaptive", in that it
determined by the data, in two distinct ways. First, if at a particular scale many observed WCs are ``large" (compared with their standard errors)
then ash infers that, at this scale, many of the true WCs may also be large - that is, the estimated distribution $g$ in (\ref{eq:ash_model_1}) will have a long tail.
Consequently ash will shrink less at this scale than at scales where few observed
WCs are large, for which the estimated $g$ will have a short tail. This is illustrated in panels b-c: at scale 1, many observed WCs are large (b), and so very little shrinkage is applied to these estimates (c).
In contrast, at scale 7, few observed WCs are large (b), and so stronger shrinkage is applied (c). Second, the shrinkage is adaptive to 
the standard error for each WC: at a given scale, WCs with larger standard error are shrunk more strongly than WCs with small standard error.
This is illustrated in panel d). (The standard errors vary among WCs here because of the hetereskedastic variance.)

@@

For the Gaussian case, we focus on mean estimation, initially with homoskedastic errors. We modelled our simulation study after
\cite{Antoniadis2001Wavelet}, using many of the same test functions, a variety of sample sizes, two different signal to noise ratios (SNRs), and including
the best-performing methods from their comparison. In particular their results showed that Translation Invariant (TI) thresholding (\cite{Coifman1995Translationinvariant}) performed the best for most of the test signals, where performance is measured by mean squared error (MSE). We also considered the Empirical Bayes shrinkage procedure (\cite{Johnstone2005Empirical}), named Ebayesthresh. 
All the methods were applied using the Symmlet8 wavelet basis \cite{Daubechies1992Ten}.

@@

We simulated data under two different scenarios:
\begin{enumerate}
\item We generated $n=500$ independent $(X_i,Y_i)$ pairs, with $X_i \sim$ Uniform(0,1), and $Y_i | X_i=x_i \sim N(m(x_i),s(x_i)^2)$
where $m(\cdot)$ and $s(\cdot)$ denote the mean and standard deviation functions (Figure \ref{fig:mfvb_eg}). We measured performance by the MSE 
evaluated at 201 equally spaced points on $(X_{min},X_{max})$ for both the mean and the standard deviation.
\item We generated $n=1024$ independent $(X_i,Y_i)$ pairs, with the $X_i$'s (deterministically) equally spaced on (0,1), and $Y_i|X_i$ as above. Performance is measured by MSE evaluated at the 1024 $X_i$'s for both the mean and the standard deviation.
\end{enumerate}
\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{mfvb_eg.pdf}
    \caption{Shows the mean function $m(x)$ $\pm$2 standard deviations $s(x)$ used in the simulation study comparing SMASH against MFVB. These functions correspond to mean and standard deviation functions (A) in Figure 5 from \cite{Menictas2015Variational}.}
    \label{fig:mfvb_eg}
\end{figure}

@@

We compared SMASH with six other methods, but we focus here on the comparisons with the best-performing other methods, which are Haar-Fisz (HF) (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}). The latter, like SMASH, is an Empirical Bayes method,  but with a less flexible prior distribution on the
multi-scale coefficients. The HF method involves first performing a transformation on the Poisson counts, and applying Gaussian wavelet methods to the transformed data. 
There are many choices for Gaussian wavelet methods, and the performance depends on these choices (and with different choices being optimal for different data sets). 
The settings we used here are documented in Supplementary Information, and were chosen by us to optimize (average) performance through moderately extensive experimentation on a range of simulations.

In summary, SMASH outperformed both HF and BMSM in the majority of simulations, with the gain in accuracy being strongest for the more challenging lower-intensity
scenarios. A typical result is shown in Figure \ref{fig:pois_sim}, with complete results in Supplementary Information. 
Among the other two methods, BMSM tends to be the more consistent performer. HF, with the settings
we used here, performs quite variably, being worse than the other two in most scenarios, but occasionally performing the best (specifically for the Angles, Bursts and Spikes test functions,
with (min,max) intensity (1/128,128)). As noted above, the HF transform can be used with many settings, so the results here should be viewed as a guide to the 
performance that can be achieved in practice.

%Besides the somewhat strong assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz. Here we analyzed primary resolution levels of 4, 5, 6 and 7, similar to \cite{Besbeas2004Comparative}. On the other hand, SMASH outperforms BMSM consistently, even though it is based on the same likelihood factorization used in the latter. We can thus conclude that the choice of ASH as the shrinkage procedure is superior to that used in BMSM in the simulation study. More importantly, using this formulation in SMASH also makes it easily extensible to multiple samples in the context of a (generalized) linear model, something we will briefly describe in the Discussion section.
\begin{figure}
\centering
		\begin{subfigure}[b]{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{bursts_pois.pdf}
        \caption{}
        \label{fig:bursts_fn}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{violin_pois_1.pdf}
        \caption{}
        \label{fig:pois_1}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{violin_pois_8.pdf}
        \caption{}
        \label{fig:pois_8}
    \end{subfigure}
    \caption{Comparison of methods for denoising Poisson data for the ``Bursts'' test function. (a) shows the (unscaled) test function. The violin plots in (b) and (c) show distributions of MISE for each method over 100 datsets, with smaller values indicating better performance. The dashed green line indicates the median MISE for SMASH. Panel (b) corresponds to a (min,max) intensity of (0.01,3), and (c) corresponds to a (min,max) intensity of (1/8,8).}
    \label{fig:pois_sim}
\end{figure}

One disadvantage of the HF transform is that, to achieve translation invariance (TI), the transform has to be done explicitly for each shift of the data: the tricks usually used to do this efficiently \cite{Coifman1995Translationinvariant} do not work here. Thus, making HF fully translation invariant increases computation by a factor of $T$, rather than the factor of $\log(T)$ for the other methods. Here we follow advice in \cite{Fryzlewicz2004HaarFisz} to reduce the computational burden by averaging over 50 shifts of the data rather than $T$. Even so, HF was substantially slower than the other methods.
 A direct comparison of computational efficiency between SMASH and BMSM is difficult, as they are coded in different programming environments. Nevertheless, similarities between the two methods suggest that they should have similar computational cost.
 Both SMASH and BMSM took, typically, less than a second per dataset in our simulations.

@@

To further illustrate our Poisson de-noising procedure we applied it to data from genomic sequencing. Specifically we applied SMASH to chromatin immunoprecipitation sequencing (ChIP-seq) data for the transcription factor {\it YY1} in cell line GM12878
collected by the ENCODE (\textbf{Enc}yclopedia \textbf{O}f \textbf{D}NA \textbf{E}lements) project. 
The data (e.g.~Figure \ref{fig:seq_peak_data}) consist of counts of sequencing reads mapping to each location in genome. These can be treated as
arising from an inhomogeneous Poisson process, whose intensity at base $b$ is related to the strength of the binding 
of the transcription factor near $b$. Because binding tends to be quite localized, the intensity is low on average (the vast majority of 
counts are 0), but has a small number of intense ``peaks". Identifying these peaks can help discover regions where 
binding occurs, which is an important component of understanding gene regulation. Consequently there are
many methods published for ``peak detection" in ChIP-Seq data \cite{Wilbanks2010Evaluation}.

@@

To illustrate this idea we applied SMASH to ChIP-seq data from a region of length $2^{17} (\approx 131k)$ basepairs from chromosome 1
(hg19 chr1:880001-1011072). The estimated intensity is shown in Figure \ref{fig:seq_peak_est}, overlaid on peaks called by
the popular peak calling software MACS \cite{Zhang2008Modelbased}. We see that the locations with the strongest SMASH intensity estimates 
corresponds to peaks found by MACS.
However, the intensity estimate also suggests the presence of several additional weaker peaks not identified by MACS.

@@

With some work, our methods could also be extended to higher dimensions, where a wider range of applications is possible. For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in \cite{Nowak1999Multiscale}. However, recent research in image denoising problems has shown that discontinuities along edges present in many images such as photographs might render wavelet transformations undesirable \cite{Cande00}. We could thus incorporate ASH into other types of transformations such as curvelets \cite{Cande00}, which would be a potential direction for future work.
\newpage
\section{Reference}

@@

With $\bm{Z}$ as defined in \eqref{eq:varobs1}, we apply the wavelet transform $W$ to $\bm{Z}^2$, and obtain the wavelet coefficients $\bm{\Gd}=W\bm{Z}^2$. Note that $\mathbb{E}(\bm{\Gd})=(\bm{\Gg})$, where $\bm{\Gg}=W\bm{\s}^2$. Again we treat the likelihood for $\bm{\Gg}$ as if it were independent, resulting in
\begin{eqnarray}
L(\bm{\Gg}|\bm{\Gd})=\prod_{j=0}^J\prod_{k=0}^{T-1}P(\Gd_{jk}|\Gg_{jk})
\end{eqnarray}
However, the likelihoods $L(\Gg_{jk}|\Gd_{jk})$ are not normal, and have no simple closed form expressions. As such, we approximate the likelihood by a normal likelihood through matching the moments of a normal distribution to the distribution $P(\Gd_{jk}|\Gg_{jk})$ i.e.
\begin{eqnarray}
P(\Gd_{jk}|\Gg_{jk})\approx N(\Gg_{jk},\hat{\mathbb{V}}(\Gd_{jk}))
\end{eqnarray}
so that
\begin{eqnarray}\label{eq:gaus approx}
L(\Gg_{jk}|\Gd_{jk})\approx \phi(\Gd_{jk};\Gg_{jk},\mathbb{V}(\Gd_{jk}))
\end{eqnarray}
where $\phi$ is the normal density function, and $\mathbb{V}(\Gd_{jk})$ is the variance of the detail coefficients. Since these variances are unknown, we estimate them from the data and then proceed to treat them as known. More specifically, since $Z_t\sim N(0,\s_t^2)$, we have that
\begin{eqnarray}
&\mathbb{E}(Z_t^4)\approx 3\s_t^4\notag\\
\label{eq:varvarest}\Rightarrow&\mathbb{V}(Z_t^2)\approx 2\s_t^4
\end{eqnarray}
and so we simply use $\frac{2}{3}Z_t^4$ as an unbiased estimator for $\mathbb{V}(Z_t^2)$. It then follows that $\hat{\mathbb{V}}(\Gd_{jk})$ is given by $\sum_{l=1}^n \frac{2}{3}Z_l^4W_{jk,l}^2$, and is unbiased for $\mathbb{V}(\Gd_{jk})$. These will be the inputs to ASH, which then produces shrunk estimates in the form of posterior means for the corresponding parameters. Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the wavelet coefficients at the finer levels. This is likely because the distribution of the wavelet coefficients is extremely skewed, especially when the true coefficients are small (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points). One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH). The final estimate of the variance function is obtained from the posterior means via the average basis inverse across all the shifts.

@@

Note here that for the reconstructed signal to possess the property of shift invariance (\cite{Coifman1995Translationinvariant}), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see \cite{Coifman1995Translationinvariant}, and \cite{Kolaczyk1999Bayesian}) rather than as described above. The idea remains the same however, and we can simply think of the extra $\Ga$'s as being defined similarly as the original $\Ga$'s, albeit from a shifted version of the original data points. To be more specific, the TI table contains the $\Ga_{jk}$ for all circulant shifts of the signal. Here we define the $t$-th shift of the signal $\bm{Y}$, denoted by $\bm{Y}^{(t)}$, to be created from $\bm{Y}$ itself by moving the first $n-t$ elements of $\bm{Y}$ $t$ positions to the right and then putting the last $t$ elements of $\bm{Y}$ in the first $t$ locations. Using this table, we are essentially computing the posterior expectations in \eqref{eq:Eproduct}-\eqref{eq:E2product} by averaging over all posterior expectations for every shift of the original signal ie.
\begin{eqnarray}
\label{eq:TIapproxexp}\frac{1}{n}\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})
\end{eqnarray}
which is an approximation to the true quantity we wish to compute, given by
\begin{eqnarray}
E(\hat{\Gl}_k)=\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})P(\mbox{$t$-th shift})
\end{eqnarray}
\end{appendices}
